%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Avery}{Harnish}{ \href{mailto:averyharnish@gmail.com}{averyharnish@gmail.com} - \href{https://averyharnish.com}{averyharnish.com} - +1.717.454.7980
}

\section{About}
\location{I'm a product-minded software engineer working on the next generation of developer tools.}

\section{Experience}

\runsubsection{Apollo GraphQL, Inc.}
\descript{- Senior Software Engineer }
\location{September 2020 - Current}
\vspace{\topsep}
Lead developer for the Rover CLI
\begin{tightemize}
\item Ported all server-side graph management utilities from the now-deprecated \href{https://github.com/apollographql/apollo-tooling}{apollo-cli} to \href{https://github.com/apollographql/rover}{Rover}.
\item Regularly communicated with product and engineering teams in order to align direction and deliver value to our developers.
\item Developed an error handling framework for \href{https://github.com/apollographql/rover}{Rover} that is complete with documented error codes and helpful suggestions for resolving frequently encountered errors.
\item Wrote extensive documentation to support developers using \href{https://github.com/apollographql/rover}{Rover} and developers working on \href{https://github.com/apollographql/rover}{Rover}.
\item Architected all of \href{https://github.com/apollographql/rover}{Rover}'s cross-platform installers.
\item Automated and documented \href{https://github.com/apollographql/rover}{Rover}'s complex release pipeline.
\item Managed \href{https://github.com/apollographql/rover}{Rover}'s open source issue tracker and community pull requests.
\end{tightemize}
\sectionsep

\runsubsection{Cloudflare, Inc.}
\descript{- Systems Engineer }
\location{November 2018 - August 2020}
\vspace{\topsep}
Core developer for the Wrangler CLI and AMP Real URL.
\begin{tightemize}
\item Designed and developed \href{https://github.com/cloudflare/wrangler}{Wrangler} with a small team.
\item Designed and developed \href{https://github.com/cloudflare/wrangler/milestone/18}{`wrangler dev`} which allows anyone to test their Workers in a local environment.
\item Contributed to Rust open source projects for Wrangler dependencies tokio, wasm-pack, cargo-generate, and binary-install.
\item Developed and maintained \href{https://workers.cloudflare.com/sites}{Workers Sites} which boasts faster response times when benchmarked against similar products such as Netlify and Zeit.
\item Created an open source \href{https://github.com/EverlastingBugstopper/worker-typescript-template}{template} for developing Cloudflare Workers with TypeScript.
\item Managed \href{https://github.com/cloudflare/wrangler}{Wrangler}'s open source issue tracker and community pull requests.
\end{tightemize}
\sectionsep

\runsubsection{Cloudflare, Inc.}
\descript{- Systems Engineer Intern }
\location{May 2018 – November 2018}
\vspace{\topsep}
Developed applications for Cloudflare's edge network with \href{https://workers.cloudflare.com}{Cloudflare Workers}.
\begin{tightemize}
\item Shipped a distributed implementation of \href{https://wicg.github.io/webpackage/draft-yasskin-http-origin-signed-responses.html}{Signed HTTP Exchanges} to provide \href{https://www.cloudflare.com/website-optimization/amp-real-url/}{Real URLs} for Cloudflare customers with AMP pages that now serves thousands of signed exchanges per second to Googlebot.
\item Spoke about AMP Real URL and signed exchanges at the AMP Contributor Summit in October of 2018.
\item Developed the \href{https://developers.cloudflare.com/workers/tooling/serverless/}{Serverless Provider Plugin} for Cloudflare Workers which was the first official CLI tool for publishing Workers.
\end{tightemize}
\sectionsep

\section{Education}
\runsubsection{Lafayette College}
\descript{- Bachelor of Arts}
\location{Computer Science and Religious Studies}
\sectionsep

\section{Relevant Skills}
\begin{minipage}[t]{.5\textwidth}
\runsubsection{Experienced with}\descript{}
Product Engineering \textbullet{} Rust \textbullet{} JavaScript \\ CI/CD \textbullet{} Cross-platform release management \\ Technical Writing \textbullet{} Cloudflare Workers\\
\sectionsep
\runsubsection{Familiar with}\descript{}
Golang \textbullet{} CSS \textbullet{} TypeScript \\ JS bundlers \textbullet{} Docker \textbullet{} Public Speaking
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.49\textwidth}
\runsubsection{Presentations}\descript{}
AMP Contributor Summit 2018 \descript{- Mountain View, CA}
\sectionsep
\runsubsection{Publications}\descript{}
Real URLs for AMP Cached Content Using Cloudflare Workers \descript{- Cloudflare Blog}
\sectionsep
\end{minipage}

\end{document} \documentclass[]{article}